---
title: "Basketball and Presidential Vote in NC"
author: "Dr. Cetinkaya-Rundel"
date: "March 23, 2015"
output:
  html_document:
    fig_height: 4
    fig_width: 8
---

```{r echo=FALSE}
library(downloader)
```

Public Policy Polling surveyed  849 registered North Carolina voters from February 24th to 26th, 2015. The full report on the poll results can be found at http://www.publicpolicypolling.com/pdf/2015/PPP_Release_NC_30515.pdf. We are going to focus on responses to the following questions:

* Who will you be rooting for in the Duke-UNC basketball game next month?
* In the last presidential election, did you vote for Barack Obama or Mitt Romney?

We want to evaluate whether college basketball allegiance of NC residents is associated with how they voted in the 2012 presidential election.

First, let's load the dataset:

```{r}
download("https://stat.duke.edu/~mc301/data/basket_pres.csv", destfile = "basket_pres.csv")
basket_pres = read.csv("basket_pres.csv")
```

The data looks like the following:
```{r}
head(basket_pres)
```


The distribution of responses is as follows:

```{r}
table(basket_pres$team, basket_pres$vote)
```

Let's reorder the levels of `team` variable to match the table given in the report:
```{r}
basket_pres$team = factor(basket_pres$team, levels = c("Duke", "UNC", "Not sure"))
```

To evaluate the relationship between these variables we need to use a chi-square independence test. Our hypotheses. We can use the `inference` function to do this.

First, let's load the inference function:

```{r}
download("https://stat.duke.edu/~mc301/R/inference.RData", destfile = "inference.RData")
load("inference.RData")
```

Then we use the familiar format of `inference(response variable, explanatory variable, ...)`:

```{r}
inference(basket_pres$team, basket_pres$vote, est = "proportion", type = "ht", alternative = "greater", method = "theoretical")
```


