---
title: "Application Exercises 4.2 and 4.3"
output:
  html_document:
    theme: cerulean
    highlight: pygments
    css: ../../../Labs/lab.css
---

## App Ex 4.2

Load the data: (I downloaded it to the "data" directory on my computer first.)
```{r}
zinc = read.csv("data/zinc.csv")
```

Since we have been talking about t-tests and paired t-tests versus t-tests for
two independent samples, first consider if this is a paired situation.  Is there
a special correspondence between the observations?  The cases are locations and
at each location there are two attributes recorded: `bottom` and `surface`
denoting concentrations at the bottom and the surface.

As I said in class on Wednesday, another useful thing to consider is what the
data frame looks like.  You can do that by clicking on `zinc` in the upper right
pane or doing

```{r, comment=NA}
zinc
```

The data frame shows that there is a special correspondence between the
concentration at the bottom and the surface, so this is paired data.

To create a new variable describing the differences and print out zinc do

```{r, comment=NA}
zinc$diff = zinc$bottom - zinc$surface
zinc
```

A new column has been added to the `zinc` data frame.  You can now
do a hypothesis test / confindece interval / whatever on the new variable
`diff`.

For the last question, what is the code to create a bootstrap distribution?  It
is something like:

```{r, comment=NA}

m               = 1000
bootstrap.means = rep(0, m)
n               = nrow(zinc)

for (i in 1:m) {
	bootstrap.sample   = sample(zinc$diff, size=n, replace=TRUE)
	bootstrap.means[i] = mean(bootstrap.sample)
}

hist(bootstrap.means)

```

```{r, echo=FALSE}
load("../../../Labs/inference/inference.RData")
```

Or, if you have loaded the inference function from Lab 7, you can do **something** like
```{r, comment=NA}
inference(y = zinc$diff, est="mean", type="ht", null=0, alternative="twosided", method="simulation")
```

## App Ex 4.3

Again, since we have been talking about t-tests and paired t-tests versus
t-tests for two independent samples, consider if this is a paired situation or
not.
