---
title: "Lab 1 - Introduction to R and RStudio"
author: KEY
output:
  html_document:
    highlight: pygments
    theme: cerulean
---

#### Load data:
```{r}
source("http://www.openintro.org/stat/data/arbuthnot.R")
```

#### Exercise 1: (2 points)

```{r}
arbuthnot$girls
```

#### Exercise 2: (2 points)
The number of girls baptized each year decreases around 1650 then starts increasing after 1660. The rate of increase slows down around 1690.

#### Exercise 3: (4 points = 2 for plot + 2 for interpretation)
The proportions of boys baptized each year are slightly over 50%. There are cyclical patterns but overall there seems to be a slight decrease in the proportions over time.

```{r fig.width=7, fig.height=5}
plot(arbuthnot$year, arbuthnot$boys/(arbuthnot$boys + arbuthnot$girls), type = "l")
```

#### Load data:
```{r}
source("http://www.openintro.org/stat/data/present.R")
```


#### Exercise 4: (2 points)

The years included in the dataset are 1940 - 2002. The data set has 63 observations and 3 variables. The variable names are year, boys, and girls.

#### Exercise 5: (2 points)  

The counts are much higher than in the Arbuthnot data set, they are not on the same scale.

#### Exercise 6: (4 points = 2 for plot + 2 for interpretation)  

Arbuthnot's observation about boys being born in greater proportion than girls holds up in the U.S. as well. However while the ratio of boys is much higher than girls in the 1940s, the ratio decreases and approaches to 50% throughout time.

```{r fig.width=7, fig.height=5}
plot(present$year, present$boys/(present$boys + present$girls), type = "l")
```

#### Exercise 7: (4 points = 2 for index + 2 for year)  

We saw the most number of births in 1961.

```{r}
which.max(present$boys + present$girls)
present$year[22]
```

