% -*- TeX-engine: xetex; eval: (auto-fill-mode 0); eval: (visual-line-mode 1); -*-
% Compile with XeLaTeX

\documentclass[11pt]{article}
\input{../app_style.tex}

%%%%%%%%%%%%%%%%
% Timing
%%%%%%%%%%%%%%%%

% 15-20 minutes

%%%%%%%%%%%%%%%%
% Sakai link for course
%%%%%%%%%%%%%%%%

% UPDATE FOR OWN COURSE
% LINK TO ASSIGNMENTS TOOL IN SAKAI

\newcommand{\Sakai}[1]
{\href{https://sakai.duke.edu/portal/site/ba0d1c18-ba55-473f-9d70-b6a1f9559bbe/page/9870858b-a1a9-481e-8497-8a6ffe9e5be2}{Sakai}}

%%%%%%%%%%%
% App Ex number    %
%%%%%%%%%%%

% DON'T FORGET TO UPDATE

\newcommand{\appno}[1]
{5.1}

%%%%%%%%%%%%%%
% Turn on/off solutions       %
%%%%%%%%%%%%%%

% Off
\newcommand{\soln}[1]{
\vskip5pt
}

%% On
%\newcommand{\soln}[1]{
%\textit{\textcolor{custom_darkGray}{#1}}
%}

%%%%%%%%%%%%%%%%
% Document
%%%%%%%%%%%%%%%%

\begin{document}
\fontspec[Ligatures=TeX]{Helvetica Neue Light}

Dr. \c{C}etinkaya-Rundel \hfill Data Analysis and Statistical Inference \\

\ttl{Application exercise \appno{}: \\
Inference for a single proportion}

\inst{Submit your responses on \Sakai{}, under the appropriate assignment. Only one submission per team is required. One team will be randomly selected and their responses will be discussed.}


\section*{How many digits of $\pi$ do Americans have memorized?}

A Survey Monkey Audience poll asked respondents to type the digits of $\pi$ from memory. The distribution of results is as follows:

\begin{center}
\begin{tabular}{l | r}
LEVEL OF  &	PERCENTAGE  \\
PRECISION & OF RESPONDENTS \\
\hline
3.1		& 73 \\
3.14		& 64 \\
\textbf{3.141}	& \textbf{33} \\
3.1415	& 26 \\
3.14159	& 19 \\
3.141592	& 12 \\
3.1415926    &	10 \\
3.14159265  &	7 \\
3.141592653 & 	5 \\
\end{tabular}
\end{center}

Survey Monkey says that their Audience surveys are benchmarked to ensure the polling pool is representative of the U.S. population.

Source: {\footnotesize \url{http://fivethirtyeight.com/datalab/how-many-digits-of-pi-you-have-to-have-memorized-to-be-special/}}

%

Don't forget to check the conditions when completing the following tasks.

\begin{enumerate}

\item You are asked to write a newspaper article about the percentage of people who have memorized digits of $\pi$ beyond the second decimal (third decimal or more). You, obviously, shouldn't just report the point estimate from the survey, but instead also provide a margin of error around it. Report the findings in one sentence at the 95\% confidence level.

\item Evaluate whether these data provide convincing evidence that less than 50\% of people have memorized digits of $\pi$ beyond the second decimal

\end{enumerate}

%

\end{document}