---
title: "Football and Politics in NC"
author: "Dr. Cetinkaya-Rundel"
date: "October 31, 2014"
output:
  html_document:
    fig_height: 4
    fig_width: 8
---

```{r echo=FALSE}
library(downloader)
```

Public Policy Polling surveyed 780 likely voters from October 16th to 18th, 2014. The full report on the poll results can be found at http://www.publicpolicypolling.com/pdf/2014/PPP_Release_NC_10201118.pdf. We are going to focus on responses to the following questions:

* Which is your favorite college football team in North Carolina?
* In the last presidential election, did you vote for Barack Obama or Mitt Romney?

We want to evaluate whether college football allegiance of NC residents is associated with how they voted in the 2012 presidential election.

First, let's load the dataset:

```{r}
download("https://stat.duke.edu/~mc301/data/fb_pol.csv", destfile = "fb_pol.csv")
fb_pol = read.csv("fb_pol.csv")
```

The distribution of responses is as follows:

```{r}
table(fb_pol$team, fb_pol$vote)
```

To evaluate the relationship between these variables we need to use a chi-square independence test. Our hypotheses. We can use the `inference` function to do this.

First, let's load the inference function:

```{r}
download("https://stat.duke.edu/~mc301/R/inference.RData", destfile = "inference.RData")
load("inference.RData")
```

Then we use the familiar format of `inference(response variable, explanatory variable, ...)`:

```{r}
inference(fb_pol$vote, fb_pol$team, est = "proportion", type = "ht", alternative = "greater", method = "theoretical")
```


